\documentclass[10pt,a4paper,ragged2e,withhyper]{altacv}

\geometry{left=1.25cm,right=1.25cm,top=1.5cm,bottom=1.5cm,columnsep=1.2cm}
\usepackage{paracol}

% Change the colours if you want to
\definecolor{ArchBlue}{HTML}{1793d0}
\definecolor{SlateGrey}{HTML}{75747c}
\definecolor{01black}{HTML}{010101}
\colorlet{tagline}{ArchBlue}
\colorlet{heading}{ArchBlue}
\colorlet{headingrule}{ArchBlue}
\colorlet{accent}{ArchBlue}
\colorlet{emphasis}{01black}
\colorlet{body}{01black}

\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}

  \begin{document}
  \name{Kyle Kirk}
  \personalinfo{%
    \email{ktkirk@explodencode.com}
    \hspace{28}
    \phone{(530) 321 7469}
    \hspace{15}
    \location{Chico, CA}
    \newline
    \homepage{<in progress> explodencode.com}
    \linkedin{kyle-kirk-90400214}
    \github{capktkirk}

    }
    \makecvheader
    
    \AtBeginEnvironment{itemize}{\small}

    \columnratio{0.6}
    
    \begin{paracol}{2}

      \cvsection{Experience}
     
     \cvevent{Information Systems Analyst I}{Superior Court of California, County of Butte}{April 2021 - Current}{Chico, CA}
      \begin{itemize}
          \item General applications analysis for troubleshooting and assisting technicians with court systems for Clerk/Bench/Admin deployment.
          \item Server management, QoS upkeep for LAN/WAN systems, VOIP stability engineering with Vertical WAVE server.
          \item Multi-site Traffic optimization and management of Remote Desktop services to allow for a seamless integration for distant or remote workers within the organization.
          \item Identify infrastructure system requirements and recommend hardware/software solutions.
          \item Configuration of network switches/ports for DHCP leases to allow Remote Desktop users access into the internal network via VPN.
          \item Monitor SaaS solutions and assist in their deployment for monitoring workstations across multiple sites. (Solarwinds, Microsoft Endpoint, Lansweeper, etc)
          \item Assisted in the designed and deployment of a solution based on Microsoft Documentation for the "PrintNightmare" CVE for court specific needs.
      \end{itemize}
            \divider
      \cvevent{Modern Framework Consultant}{Self}{August 2020 - April 2021}{Chico, CA}
      \begin{itemize}
          \item Consulting different clients on web based solutions for their communication needs.
          \item Creating a modern interface for a Día de los Muertos informational site for a local Spanish immersion school.
          \item \href{https://www.culturamapache.com}{(Link) Rosedale Cultura Mapache Site}
      \end{itemize}
      \divider
      \cvevent{Grader and Teacher's Assistant}{Chico State}{January 2019 -- June 2021}{Chico, CA}
      \begin{itemize}
        \item Grading for a writing intensive course on futurism \& technology.
        \item Grading, tutoring, \& teacher's assistant for a 500-level course in compiler design \& optimization.
        \item Teacher's assistant for 200-level course in programming \& algorithms.
        \item Grading \& teacher's assistant for a 100-level course for programming \& algorithms.
      \end{itemize}

      \divider

      \cvevent{Client Assistant}{We Care A Lot Foundation}{August 2019 -- July 2020}{Chico, CA}
      \begin{itemize}
        \item Driving disabled clients to arts and crafts shows so that they could set up their wares. Also handled purchasing and inventory management.
      \end{itemize}


      \switchcolumn

      \cvsection{General Skills}
      \color{01black}
      \cvtag{Leadership}
      \cvtag{Firewalls/Network Security}
      \newline
      \cvtag{QoS}
      \cvtag{Command line}
      \cvtag{Scripting} 
      \newline
      \cvtag{\href{http://github.com/capktkirk/resume}{Recursion:github.com/capktkirk/resume}}
      \newline
      \cvtag{Infrastructure Management/Optimization}
      \cvtag{Networks}
      \cvtag{Continuous Integration}
      \newline
      \cvtag{Project Management}
    \cvtag{App Development}
      \cvtag{Continuous Integration}
      \newline
            \cvtag{Sales}
      \cvtag{Team Coordination}
      \newline
      \cvtag{Documentation}
      \cvtag{Debugging}
      \newline
      \cvtag{Server Maintenance}

      \cvsection{Technical Skills}
      \textbf{Programming Languages: }
      \newline
      \cvtag{C++}
      \cvtag{C}
      \cvtag{C\#}
      \cvtag{Python}
      \cvtag{Flutter} 
      \cvtag{Golang} 
      \cvtag{Bash}
      \cvtag{Javascript}
      \newline
      \divider
      \newline
      \textbf{Database/Platforms:}
      \newline
      \cvtag{MySQL} 
      \cvtag{MongoDB} 
      \cvtag{AWS}
      \cvtag{Linux}
      \cvtag{GCP}
      \cvtag{GIT}
      \cvtag{Docker}
      \newline


      \cvsection{References}

      \cvref{Prof. Todd A. Gibson}{Chico State University}{tagibson@csuchico.net}
      \divider
      \cvref{J. Boyd Trolinger}{Butte College}{jboydt@foobt.net}
      \cvsection{Education}

      \cvevent{B.S.\ in Computer Science}{Chico State University}{}

      \divider

      \cvevent{A.S.\ in Computer Science}{Butte Community College}{}
      
    \end{paracol}
    \pagebreak
    \cvsection{Extra Curricular}

    \cvevent{Founder and President of the CodeRunners (Club)}{Butte College}{January 2016 -- March 2018}{Chico, CA}
    \begin{itemize}
      \item Created projects and led instruction in Python 3.x for members.
      \item Organized codeathons for projects and team building.
      \item Created documentation for standard coding practices.
      \item Utilized Raspberry Pi 2/3's to create a magic mirror project for Butte College.
    \end{itemize}
    \cvsection{Clubs, Associations \& Honors}
    \begin{itemize}
        \item Member of Association of Computing Machinery (ACM : http://chico-acm.com/)
        \item Member of Honors Society Upsilon Pi Epsilon (UPE : https://upe.acm.org/)
        \item Member of the Usr0 Security Club
        \item Placed in the top 15\% during the National Cyber Security League in Spring of 2019 with a student led team.
        \item Owner/Organizer of student-run COVID-19 Discord server used to assist in the remote learning and networking of students.
    \end{itemize}
  \end{document}


