%%%%%%%%%%%%%%%%%
% This is an example CV created using altacv.cls (v1.3, 10 May 2020) written by
% LianTze Lim (liantze@gmail.com), based on the
% Cv created by BusinessInsider at http://www.businessinsider.my/a-sample-resume-for-marissa-mayer-2016-7/?r=US&IR=T
%
%% It may be distributed and/or modified under the
%% conditions of the LaTeX Project Public License, either version 1.3
%% of this license or (at your option) any later version.
%% The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.3 or later is part of all distributions of LaTeX
%% version 2003/12/01 or later.
%%%%%%%%%%%%%%%%

\documentclass[10pt,a4paper,ragged2e,withhyper]{altacv}

\geometry{left=1.25cm,right=1.25cm,top=1.5cm,bottom=1.5cm,columnsep=1.2cm}
\usepackage{paracol}
\ifxetexorluatex
  \setmainfont{Lato}
\else
  \usepackage[default]{lato}
\fi

\definecolor{VividPurple}{HTML}{3E0097}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
\colorlet{tagline}{VividPurple}
\colorlet{heading}{VividPurple}
\colorlet{headingrule}{VividPurple}
\colorlet{accent}{VividPurple}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}

\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}

\begin{document}
\name{Kyle Kirk}
\personalinfo{%
  \email{ktkirk@explodencode.com}
  \phone{(530) 321-7469}
  \mailaddress{75 Harvest Park Court, Apt 119}
  \location{Chico, CA}
  \homepage{<in progress> explodencode.com}
  \linkedin{kyle-kirk-90400214}
  \github{github.com/capktkirk}

}

\makecvheader

\AtBeginEnvironment{itemize}{\small}

\columnratio{0.6}

\begin{paracol}{2}

\cvsection{Experience}

\cvevent{Grader and Teachers Assistant}{Chico State}{January 2019 -- Ongoing}{Chico, CA}
\begin{itemize}
\item Grading for a writing intensive course on futurism \& technology.
\item Grading for a 500 level course in Compiler Design \& Optimization, as well as tutoring and being a teachers assistant.
\item Grading for a 100 level course for programming \& algorithms, as well as being a teachers assistant.
\end{itemize}

\divider

\cvevent{Client Assistant}{We Care A Lot Foundation}{August 2019 -- July 2020}{Chico, CA}
\begin{itemize}
\item Driving disabled clients to art and crafts shows so that they could set up their wares, as well as handling the purchasing and inventory management.
\end{itemize}

\cvevent{Private Tutor}{Self}{Aug 2017 - Ongoing}{Chico, CA}
\begin{itemize}
\item Tutoring students in Python, C++, Flutter, Golang as well as general computing philosophies and discrete mathematics.
\end{itemize}


\cvsection{Education}

\cvevent{B.S. \ in Computer Science}{Chico State University}{Sept 2018 -- June 2021}{}

\divider

\cvevent{A.S.\ in Computer Science}{Butte Community College}{January 2016 -- May 2018}{}

\switchcolumn

\cvsection{Life Philosophy}
\begin{quote}
``Seven times down, eight times up.''
\end{quote}

\cvsection{Strengths}

\cvtag{Leadership}
\cvtag{Debate}
\cvtag{Organization}\
\cvtag{Tenacity}
\cvtag{Patience}

\divider\smallskip

\cvtag{Code Review}
\cvtag{Command line}
\cvtag{Scripting} \
\cvtag{Recursion -> github.com/capktkirk/resume}

\cvsection{Technical Skills}

\cvskill{C++}{4}
\cvskill{Python}{4}
\cvskill{Linux/Bash}{4}
\cvskill{Golang}{3}
\cvskill{Git}{3}
\cvskill{C}{3}
\cvskill{Flutter}{3}
\cvskill{AWS/GCP}{2}
\cvskill{LaTeX}{2}

\cvsection{Other Skills}

\cvskill{Sales}{4}
\cvskill{Team Coordination}{4}


\cvsection{References}

\cvref{Prof. Todd A. Gibson}{Institute}{tagibson@csuchico.net}
\divider
\cvref{J. Boyd Trolinger}{Butte College}{jboydt@foobt.net}
\divider

\end{paracol}

\cvsection{Extra Curricular}

\cvevent{Founder and President}{Butte College}{January 2016 -- March 2018}{Chico, CA}
\begin{itemize}
\item Created projects and led instruction in Python 3.x for members.
\item Organized codeathons for projects and team building.
\item Created documentation for standard coding practices.
\item Utilized Raspberry Pi 2/3's to create a magic mirror project for Butte College.
\ed{itemize}

\end{document}
